Analyse from review

### 2021-02-20 manuscript/bef_stability/fig1_biomass_network.Rmd
Finalize figures

```{r pca}
myload(habitat_press, dir = mypath("data"))
library(sf)
library(ggspatial)
# map
myload(p_st, dir = mypath("manuscript", "bef_stability", "figs"))
# Station
myload(biomass_ts_sax, op_analysis, dir = mypath("data"))
op_analysis_bbb <- filter(op_analysis, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
station <- get_basin_station(sf_obj = TRUE)
station %<>%
  filter(station %in% unique(op_analysis$station))
## Get bbb
station %<>%
  mutate(type = ifelse(
      station %in% unique(op_analysis_bbb$station),
      "stable", "unstable"),
    st_temporal = ifelse(station %in% qt_station$station, TRUE, FALSE)
  )

@@

qt_station <- sem_data %>%
  filter(station %in% c(first_st$station[5], last_st$station[5])) %>%
  dplyr::select(station, bm_std_stab)
mysave(qt_station, dir = mypath("data"), overwrite = TRUE)

p_st <- p_st + 
  theme_void() +
  theme(plot.margin = theme_get()$plot.margin, legend.position = "none")

p_st2 <- p_st +
  geom_sf(data = filter(station, type == "stable"), color = "black") +
  geom_sf(data = filter(station, station %in% qt_station$station),
    color = "red", size = 3) +
  geom_sf_text(data = filter(
      station, station %in% qt_station$station
      ), 
    aes(label = c("C", "D")),
    #color = "red",
    fontface = 2,
    size = 5,
    nudge_x = c(-30000, 30000),
    nudge_y = c(30000, -30000)
    ) +
  coord_sf(
    xlim = c(60000, 1100000),
    ylim = c(6100000, 7122216),
    datum = sf::st_crs(2154),
    crs = 2154,
    expand = FALSE
  )

@@

)
fig1c
save_plot("figs/fig1c_low_rich.png", fig1c,
  nrow = 2, 
  ncol = 1,
  base_height = 4,
  base_width = 7
)
```

@@

)
save_plot("figs/fig1d_high_rich.png", fig1d,
  nrow = 2, 
  ncol = 1,
  base_height = 4,
  base_width = 7
)
```

@@

save_plot(mypath("manuscript", "bef_stability", "figs/fig1.png"), fig1_draw_test,
nrow = 3, 
  ncol = 1,
  base_height = 4,
  base_width = 10 
)
```

>>>>

```{r pca}
myload(habitat_press, dir = mypath("data"))
library(sf)
library(ggspatial)
# map
myload(p_st, dir = mypath("manuscript", "bef_stability", "figs"))
qt_station <- sem_data %>%
  filter(station %in% c(first_st$station[5], last_st$station[5])) %>%
  dplyr::select(station, bm_std_stab)
mysave(qt_station, dir = mypath("data"), overwrite = TRUE)
# Station
myload(biomass_ts_sax, op_analysis, dir = mypath("data"))

op_analysis_bbb <- filter(op_analysis, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
station <- get_basin_station(sf_obj = TRUE)
station %<>%
  filter(station %in% unique(op_analysis$station))
## Get bbb
station %<>%
  mutate(type = ifelse(
      station %in% unique(op_analysis_bbb$station),
      "stable", "unstable"),
    st_temporal = ifelse(station %in% qt_station$station, TRUE, FALSE)
  )

@@

p_st2 <- p_st +
  geom_sf(data = filter(station, type == "stable"), color = "black") +
  geom_sf(data = filter(station, station %in% qt_station$station),
    color = "red", size = 3) +
  geom_sf_text(data = filter(
      station, station %in% qt_station$station
      ), 
    aes(label = c("C", "D")),
    #color = "red",
    fontface = 2,
    size = 5,
    nudge_x = c(-30000, 30000),
    nudge_y = c(30000, -30000)
    ) +
  coord_sf(
    xlim = c(60000, 1100000),
    ylim = c(6100000, 7122216),
    datum = sf::st_crs(2154),
    crs = 2154,
    expand = FALSE
  ) +
  theme_void() +
  theme(plot.margin = theme_get()$plot.margin, legend.position = "none")

@@

)
fig1c
save_plot("figs/fig1c_low_rich.pdf", fig1c,
  nrow = 2, 
  ncol = 1,
  base_height = 4,
  base_width = 7
)
```

@@

)
save_plot("figs/fig1d_high_rich.pdf", fig1d,
  nrow = 2, 
  ncol = 1,
  base_height = 4,
  base_width = 7
)
```

@@

save_plot(mypath("manuscript", "bef_stability", "figs/fig1.pdf"), fig1_draw_test,
nrow = 3, 
  ncol = 1,
  base_height = 4,
  base_width = 10 
)
```

### 2021-02-20 manuscript/bef_stability/manuscript.Rmd
Finalize figures

Temporal biomass stability was defined as the inverse of biomass variability.
Variability was computed as Coefficient of Variation (CV) of the biomass over
time ($CV_i = \sigma_i \mu_i^{-1}$, with $\sigma_i$ and $\mu_i$ being
respectively the standard deviation and the temporal average of the annual total
biomass of the station $i$). Then, temporal stability was equal to $CV^{-1} =
\mu \sigma^{-1}$.

@@

$$
CV_{com, i} = \overline{CV_{sp, i}} \times \sqrt{\phi_i}
$$

@@

$$
\overline{CV_{sp, i}} = \sum_k{\frac{B_{k,i} {CV}_{k, i}}{\sum_k{B_{k,i}}}}
$$

$$
\phi_i = \frac{\sigma^2_{x_{T,i}}}{(\sum_k{\sqrt{\sigma^2_{x_{k,i}}}})^2} = \frac{\sigma^2_{x_{T,i}}}{(\sum_k{\sigma_{x_{k,i}}})^2}
$$

@@

The structural equation models were based on Gaussian linear mixed-effects models. All variables
except the connectance and average trophic level
were log-transformed to fulfill model assumptions (see residual plots and data
transformation in Fig. S5 and S6, Table S5, appendix B). We set the seven
hydrographic basins as a random effect on the intercept to
account for their heterogeneity. We checked for the absence of multicollinearity 
with Variance Inflation Factor (VIF, Table S6, appendix B). The slopes reported
in the main text were standardized in order to compare their magnitude ($r_\delta
= \beta \frac{\sigma_x}{\sigma_y}$, $\beta$ being the unstandardized slope,
$\sigma_x$ and $\sigma_y$ being respectively the standard deviation of the
predictive variable $x$ and of the response variable $y$). The paths whose
slope had a $P$ value inferior or equal to $0.05$ were reported in the main text, all the
path values are presented in Table S7 and S8.

@@

The positive effect of species richness on
$\overline{CV_{sp}}$, thereby decreasing stability, is more intriguing. While
studies focusing on single-trophic communities have reported mixed effects of
species richness on $\overline{CV_{sp}}$, with destabilising effects of species
richness at population level in grasslands [@jiang_different_2009;
@gross_species_2014], a previous meta-analysis suggested that species richness had
often a positive effect on population stability in multi-trophic communities
[@jiang_different_2009].
In food-webs, theoretical models predict that the relationship between temporal
stability of populations and species richness depends on interaction strength
and its distribution [@mccann_reevaluating_1997; @thebault_trophic_2005;
@downing_temporal_2020], with stronger interactions promoting a negative
relationship between species richness and stability. Therefore, it is possible
that our results are due to strong trophic interactions, leading to more
fluctuations in population biomass, but this hypothese was not testable with the
available dataset.

@@

In contrast with previous studies, we found that the average population
variability ($\overline{CV_{sp}}$) had a stronger negative effect on community biomass
stability than synchrony [@tilman_biodiversity_2006;
@olivier_urbanization_2020]. It explains why we observe a negative effect of
species richness on temporal stability of community biomass. The weaker effect of synchrony
might be explained by the presence of generalist predators in stream
communities, which can promote synchrony between prey species that share the
same predator and thus reduces compensatory
population dynamics [@raimondo_interspecific_2004]. Alternatively, it is
possible that, in aquatic food-webs, the occurrence of large oscillatory dynamics
 leads to a higher contribution of population
variability rather than synchrony to community stability
[@mccann_reevaluating_1997]. How both strengths of interactions and the relative
contribution of synchrony and population variability to overall stability vary
between food-webs and single trophic communities is still an open question.

>>>>

Temporal biomass stability was defined as the inverse of biomass variability.
Variability was computed as Coefficient of Variation (CV) of the biomass over
time ($CV_i = \sigma_i \mu_i^{-1}$, with $\sigma_i$ and $\mu_i$ being
respectively the standard deviation and the temporal average of the annual total
biomass of the station $i$). Then, temporal stability ($S_i$) was equal to $CV^{-1} =
\mu \sigma^{-1}$.

@@

\begin{equation} 
  CV_{com, i} = \overline{CV_{sp, i}} \times \sqrt{\phi_i}
  (\#eq:cvcom)
\end{equation}

@@

\begin{equation} 
\overline{CV_{sp, i}} = \sum_k{\frac{B_{k,i} {CV}_{k, i}}{\sum_k{B_{k,i}}}}
(\#eq:cvsp)
\end{equation}

\begin{equation} 
\phi_i = \frac{\sigma^2_{x_{T,i}}}{(\sum_k{\sqrt{\sigma^2_{x_{k,i}}}})^2} = \frac{\sigma^2_{x_{T,i}}}{(\sum_k{\sigma_{x_{k,i}}})^2}
(\#eq:phi)
\end{equation}

In further analysis, we linearized the mathematical relationship linking
temporal stability to $\overline{CV_{sp, i}}$ and $\phi$ by taking the log of
temporal stability:

\begin{equation} 
  \begin{aligned}
    S_i &= (\overline{CV_{sp, i}} * \phi_i^\frac{1}{2})^{-1} \\
    \log S_i &= - \log (\overline{CV_{sp, i}} * \phi_i^\frac{1}{2}) \\
    \log S_i &= - \log (\overline{CV_{sp, i}} - \log \phi_i^\frac{1}{2} \\
    \log S_i &= - \log \overline{CV_{sp, i}} - \frac{1}{2} \log \phi_i \\
  \end{aligned}
  (\#eq:stab)
\end{equation}

@@

The structural equation models were based on Gaussian linear mixed-effects models. All variables
except the connectance and average trophic level
were log-transformed to fulfill model assumptions (see residual plots and data
transformation in Fig. S5 and S6, Table S5, appendix B). We set the seven
hydrographic basins as a random effect on the intercept to
account for their heterogeneity. We checked for the absence of multicollinearity 
with Variance Inflation Factor (VIF, Table S6, appendix B). The slopes reported
in the main text were standardized in order to compare their magnitude ($r_\delta
= \beta \frac{\sigma_x}{\sigma_y}$, $\beta$ being the unstandardized slope,
$\sigma_x$ and $\sigma_y$ being respectively the standard deviation of the
predictive variable $x$ and of the response variable $y$). Therefore, the
standardized coefficients expressed the variation of $x$ and $y$ in standard
deviation units. According to the equation (\@ref(eq:stab)), the unstandardized
coefficients of synchrony and $\overline{CV_{sp}}$ determining temporal
stability of biomass are respectively $-0.5$ and $1.0$. When standardized, a 
comparaison of those coefficients comes down to a comparaison of the standard
deviation of these two variables. The paths whose slope had a $P$ value inferior
or equal to $0.05$ were reported in the main text, all the path values are
presented in Table S7 and S8.

@@

The positive effect of species richness on
$\overline{CV_{sp}}$, thereby decreasing stability, is more intriguing. While
studies focusing on single-trophic communities have reported mixed effects of
species richness on $\overline{CV_{sp}}$, with destabilising effects of species
richness at population level in grasslands [@jiang_different_2009;
@gross_species_2014], a previous meta-analysis suggested that species richness had
often a positive effect on population stability in multi-trophic communities
[@jiang_different_2009].
In food-webs, theoretical models predict that the relationship between temporal
stability of populations and species richness depends on interaction strength
and its distribution [@mccann_reevaluating_1997; @thebault_trophic_2005;
@downing_temporal_2020], with stronger interactions promoting a negative
relationship between species richness and stability. Therefore, it is possible
that our results are due to strong trophic interactions, leading to more
fluctuations in population biomass, but this hypothese was not testable with the
available dataset.  Alternatively, our results might be explain by the effect of
increasing species richness which can increase demographic stochasticity.

@@

The population variability and synchrony are mathematically linked to the
stability of community biomass (see Methods), so the comparaison of their effect
reflected that the the comparaison of their variability. In contrast with
previous studies, we found that the average population variability
($\overline{CV_{sp}}$) had a stronger negative effect on the stability of
community biomass than synchrony [@olivier_urbanization_2020], meaning that the
variability of synchrony was equivalent the one of population variability. It
explains why we observe a negative effect of species richness on temporal
stability of community biomass whereas species richness had a strong negative
effect of synchrony. The lower variability of synchrony might be explained by
the presence of generalist predators in stream communities, which can promote
synchrony between prey species that share the same predator and thus reduces
compensatory population dynamics [@raimondo_interspecific_2004]. Alternatively,
it is possible that, in aquatic food-webs, the occurrence of large oscillatory
dynamics leads to a higher variability of population variability rather than
synchrony to community stability [@mccann_reevaluating_1997]. How both strengths
of interactions and the relative contribution of synchrony and population
variability to overall stability vary between food-webs and single trophic
communities is still an open question.

Our results raise the question of the fundamental differences between single and
multi-trophic communities. Some mechanisms are transferable from the first to
the second such higher connectance which might translate in higher competition
between consumers and thus destabilise populations [@thebault_trophic_2005].
However, the existence of top-down and bottom-up effects are obviously typical
to multi-trophic communities. The population at the top of a food-web are
limited by the growth of its prey (bottom-up effects) while the lower trophic
levels are limited by both their predators (top-down effect) and their preys
(bottom-up effects). We can conjecture that the stability of food-webs mainly
controlled by bottom-up effects will display higher synchrony while  mainly
controlled by the food-webs mainly controlled by top-down effects will display
higher population variability.

### 2021-02-20 manuscript/bef_stability/review_analysis.Rmd
Finalize figures

# SD de la variable de Olivier et al. (2020):  
sd(log(1 / sem_data$sync))
sd(log(1 / sem_data$cv_sp))
```

>>>>

# Standard deviation according to Olivier et al. (2020):
sd(log(1 / sem_data$sync))
sd(log(1 / sem_data$cv_sp))
mod_olivier <- lm(I(-log(bm_std_stab)) ~ 0 + I(-log(cv_sp)) + I(-log(sync)), data = sem_data)
broom::tidy(mod_olivier)
